---
title: "Report"
author: "Linh Nguyen"
date: "11/30/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, error = FALSE)
```

# Set up

```{r meta, results = FALSE}
# META ====
# > Libraries ----
library(tidyverse)
library(apaTables)
library(caret)
library(faraway)
library(ggplot2)
library(cplm) #for tweedie 
library(logistf) #for firth
set.seed(8051)
options(scipen = 999)

# > Data ----
data <- read.csv("InsNova_train.csv")
data$veh_body <- as.factor(data$veh_body)
data$gender <- as.factor(data$gender)
data$area <- as.factor(data$area)

submit <- read.csv("InsNova_test.csv")
```

# Bivariate correlations

```{r descriptives}
data %>% select(veh_value, exposure, veh_age, dr_age, claim_ind, claim_count, claim_cost) %>% 
  apa.cor.table()
```

# Model fitting

## Split data for cross-validation

```{r cv}
training <- data$claim_cost %>% 
  createDataPartition(p = 0.8, list = FALSE)
train <- data[training,]
test <- data[-training,]
```

## Function for Gini index

```{r gini}
normalizedGini <- function(aa, pp) {
  Gini <- function(a, p) {
    if (length(a) !=  length(p)) stop("Actual and Predicted need to be equal lengths!")
    temp.df <- data.frame(actual = a, pred = p, range=c(1:length(a)))
    temp.df <- temp.df[order(-temp.df$pred, temp.df$range),]
    population.delta <- 1 / length(a)
    total.losses <- sum(a)
    null.losses <- rep(population.delta, length(a)) 
    accum.losses <- temp.df$actual / total.losses 
    gini.sum <- cumsum(accum.losses - null.losses) 
    sum(gini.sum) / length(a)
  }
  Gini(aa,pp) / Gini(aa,aa)
}
```

## Predict claim indicator `claim_ind` with Firth regression

```{r ind}
mInd <- logistf(claim_ind ~ veh_value + exposure + veh_body + veh_age + 
                  gender + area + dr_age, 
                data = train)
summary(mInd)

mIndCoef <- mInd$coefficients[-1]

#function to compute predicted values
indpred <- function(newdata){
  newdata <- newdata %>% mutate(
  veh_body_coef = ifelse(veh_body == "BUS", 0,
                     ifelse(veh_body == "CONVT" , mIndCoef[[3]],
                        ifelse(veh_body == "COUPE" , mIndCoef[[4]],
                           ifelse(veh_body == "HBACK" , mIndCoef[[5]],
                              ifelse(veh_body == "HDTOP" , mIndCoef[[6]],
                                 ifelse(veh_body == "MCARA" , mIndCoef[[7]],
                                    ifelse(veh_body == "MIBUS" , mIndCoef[[8]],
                                       ifelse(veh_body == "PANVN" , mIndCoef[[9]],
                                          ifelse(veh_body == "RDSTR" , mIndCoef[[10]],
                                             ifelse(veh_body == "SEDAN" , mIndCoef[[11]],
                                                ifelse(veh_body == "STNWG" , mIndCoef[[12]],
                                                   ifelse(veh_body == "TRUCK" , mIndCoef[[13]],
                                                      ifelse(veh_body == "UTE" , mIndCoef[[14]], 
                                                         NA))))))))))))))
newdata <- newdata %>% mutate(
  area_coef = ifelse(area == "A", 0,
                     ifelse(area == "B", mIndCoef[[17]],
                            ifelse(area == "C", mIndCoef[[18]],
                                   ifelse(area == "D", mIndCoef[[19]],
                                          ifelse(area == "E", mIndCoef[[20]],
                                                 ifelse(area == "F", mIndCoef[[21]],
                                                        NA)))))))
newdata <- newdata %>% mutate(
  gender_coef = ifelse(gender == "F", 0, mIndCoef[[16]]))

newdata <- newdata %>% mutate(
  indPred = faraway::ilogit(mIndCoef[[1]] * veh_value + mIndCoef[[2]] * exposure + 
    veh_body_coef + veh_age * mIndCoef[[15]] + gender_coef + area_coef + dr_age * mIndCoef[[22]]))

newdata %>% select(-veh_body_coef, -area_coef, -gender_coef)
} 

train <- indpred(train)
data.frame( R2 = R2(train$indPred, train$claim_ind),
            RMSE = RMSE(train$indPred, train$claim_ind),
            NRMSE = RMSE(train$indPred, train$claim_ind)/(max(train$claim_ind) - min(train$claim_ind)),
            MAE = MAE(train$indPred, train$claim_ind),
            Gini = normalizedGini(train$indPred, train$claim_ind))

test <- indpred(test)
data.frame( R2 = R2(test$indPred, test$claim_ind),
            RMSE = RMSE(test$indPred, test$claim_ind),
            NRMSE = RMSE(test$indPred, test$claim_ind)/(max(test$claim_ind) - min(test$claim_ind)),
            MAE = MAE(test$indPred, test$claim_ind),
            Gini = normalizedGini(test$claim_ind,test$indPred))
```

## Predict number of claims `claim_count` with Tweedie model

```{r count}
mCount <- cpglm(claim_count ~ veh_value + exposure + veh_body + veh_age + 
                  gender + area + dr_age + claim_ind, 
                link = "log", data = train)
summary(mCount)

predictions <- mCount %>% predict(train)
data.frame( R2 = R2(predictions, train$claim_count),
            RMSE = RMSE(predictions, train$claim_count),
            NRMSE = RMSE(predictions, train$claim_count)/(max(train$claim_count)-min(train$claim_count)),
            MAE = MAE(predictions, train$claim_count),
            Gini = normalizedGini(predictions, train$claim_count))

predictions <- mCount %>% predict(test)
data.frame( R2 = R2(predictions, test$claim_count),
            RMSE = RMSE(predictions, test$claim_count),
            NRMSE = RMSE(predictions, test$claim_count)/(max(test$claim_count)-min(test$claim_count)),
            MAE = MAE(predictions, test$claim_count),
            Gini = normalizedGini(test$claim_count, predictions))
```

## Predict cost `claim_cost` with Tweedie model

### Including `claim_count` and `claim_ind`

```{r cost with ind}
miCost <- cpglm(claim_cost ~ veh_value + exposure + veh_body + veh_age + 
                  gender + area + dr_age + claim_ind + claim_count, 
                link = "log", data = train)
summary(miCost)

predictions <- miCost %>% predict(train)
data.frame( R2 = R2(predictions, train$claim_cost),
            RMSE = RMSE(predictions, train$claim_cost),
            NRMSE = RMSE(predictions, train$claim_cost)/(max(train$claim_cost)-min(train$claim_cost)),
            MAE = MAE(predictions, train$claim_cost),
            Gini = normalizedGini(predictions, train$claim_cost))

predictions <- miCost %>% predict(test)
data.frame( R2 = R2(predictions, test$claim_cost),
            RMSE = RMSE(predictions, test$claim_cost),
            NRMSE = RMSE(predictions, test$claim_cost)/(max(test$claim_cost)-min(test$claim_cost)),
            MAE = MAE(predictions, test$claim_cost),
            Gini = normalizedGini(test$claim_cost, predictions))

# performance in dataset without count and ind
testEmpty <- data[-training,] %>% select(-claim_ind, -claim_count, -claim_cost)

testEmpty <- indpred(testEmpty)
names(testEmpty)[names(testEmpty) == "indPred"] <- "claim_ind"
testEmpty$claim_count <- mCount %>% predict(testEmpty)
testEmpty$claim_cost <- miCost %>% predict(testEmpty)

data.frame( R2 = R2(testEmpty$claim_cost, test$claim_cost),
            RMSE = RMSE(testEmpty$claim_cost, test$claim_cost),
            NRMSE = RMSE(testEmpty$claim_cost, test$claim_cost)/(max(test$claim_cost)-min(test$claim_cost)),
            MAE = MAE(testEmpty$claim_cost, test$claim_cost),
            Gini = normalizedGini(test$claim_cost, testEmpty$claim_cost))
```

### Including `claim_count` but not `claim_ind`

```{r cost without ind}
mCost <- cpglm(claim_cost ~ veh_value + exposure + veh_body + veh_age + 
                  gender + area + dr_age + claim_count, 
                link = "log", data = train)
summary(mCost)

predictions <- mCost %>% predict(train)
data.frame( R2 = R2(predictions, train$claim_cost),
            RMSE = RMSE(predictions, train$claim_cost),
            NRMSE = RMSE(predictions, train$claim_cost)/(max(train$claim_cost)-min(train$claim_cost)),
            MAE = MAE(predictions, train$claim_cost),
            Gini = normalizedGini(predictions, train$claim_cost))

predictions <- mCost %>% predict(test)
data.frame( R2 = R2(predictions, test$claim_cost),
            RMSE = RMSE(predictions, test$claim_cost),
            NRMSE = RMSE(predictions, test$claim_cost)/(max(test$claim_cost)-min(test$claim_cost)),
            MAE = MAE(predictions, test$claim_cost),
            Gini = normalizedGini(predictions, test$claim_cost))

# performance in dataset without count and ind
testEmpty <- data[-training,] %>% select(-claim_ind, -claim_count, -claim_cost)

testEmpty <- indpred(testEmpty)
names(testEmpty)[names(testEmpty) == "indPred"] <- "claim_ind"
testEmpty$claim_count <- mCount %>% predict(testEmpty)
testEmpty$claim_cost <- mCost %>% predict(testEmpty)

data.frame( R2 = R2(testEmpty$claim_cost, test$claim_cost),
            RMSE = RMSE(testEmpty$claim_cost, test$claim_cost),
            NRMSE = RMSE(testEmpty$claim_cost, test$claim_cost)/(max(test$claim_cost)-min(test$claim_cost)),
            MAE = MAE(testEmpty$claim_cost, test$claim_cost),
            Gini = normalizedGini(test$claim_cost, testEmpty$claim_cost))
```

### Including `id` as artificial inflation

```{r cost id}
midCost <- cpglm(claim_cost ~ veh_value + exposure + veh_body + veh_age + 
                   gender + area + dr_age + claim_ind + claim_count + id, 
                 link = "log", data = train)
summary(midCost)

predictions <- midCost %>% predict(train)
data.frame( R2 = R2(predictions, train$claim_cost),
            RMSE = RMSE(predictions, train$claim_cost),
            NRMSE = RMSE(predictions, train$claim_cost)/(max(train$claim_cost)-min(train$claim_cost)),
            MAE = MAE(predictions, train$claim_cost),
            Gini = normalizedGini(predictions, train$claim_cost))

predictions <- midCost %>% predict(test)
data.frame( R2 = R2(predictions, test$claim_cost),
            RMSE = RMSE(predictions, test$claim_cost),
            NRMSE = RMSE(predictions, test$claim_cost)/(max(test$claim_cost)-min(test$claim_cost)),
            MAE = MAE(predictions, test$claim_cost),
            Gini = normalizedGini(test$claim_cost, predictions))

# performance in dataset without count and ind
testEmpty <- data[-training,] %>% select(-claim_ind, -claim_count, -claim_cost)

testEmpty <- indpred(testEmpty)
names(testEmpty)[names(testEmpty) == "indPred"] <- "claim_ind"
testEmpty$claim_count <- mCount %>% predict(testEmpty)
testEmpty$claim_cost <- midCost %>% predict(testEmpty)

data.frame( R2 = R2(testEmpty$claim_cost, test$claim_cost),
            RMSE = RMSE(testEmpty$claim_cost, test$claim_cost),
            NRMSE = RMSE(testEmpty$claim_cost, test$claim_cost)/(max(test$claim_cost)-min(test$claim_cost)),
            MAE = MAE(testEmpty$claim_cost, test$claim_cost),
            Gini = normalizedGini(test$claim_cost, testEmpty$claim_cost))
```


# Submission

```{r submit}
submit <- indpred(submit)
names(submit)[names(submit) == "indPred"] <- "claim_ind"
submit$claim_count <- mCount %>% predict(submit)
submit$claim_cost <- miCost %>% predict(submit)

submit$id <- 1:nrow(submit)
submit <- submit %>% select(id, claim_cost)

summary(submit$claim_cost)
```

